FictionEro - Affective Impact of Fiction

### 2025-06-11 study1/analysis/2_emotions.qmd
minor

marginaleffects::avg_slopes(m, variables="Condition", by="Sex", re.form=NA) |> 
  results_table()
```

@@

pred1 <- 
  rbind(
  modelbased::estimate_means(m_Arousal, by=c("Sex", "Relevance", "Condition")) |>
  as.data.frame() |> 
  mutate(Outcome="Arousal"),
  modelbased::estimate_means(m_enticement, by=c("Sex", "Relevance", "Condition") |>
  as.data.frame() |> 
  mutate(Outcome="Enticement"),
  modelbased::estimate_means(m_valence, by=c("Sex", "Relevance", "Condition")) |>
  as.data.frame() |> 
  mutate(Outcome="Valence")
)

@@

p1 <- pred1 |>
  mutate(Sex = fct_relevel(Sex, "Male", "Female")) |> 
  ggplot(aes(x=Relevance, y=estimate)) +
  geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.2) +
  geom_pointrange(aes(ymin = conf.low, ymax=conf.high, color=Condition), position = position_dodge(width=0.2), size=0.2) +
  geom_text(data=stars1, aes(y=y, label=label), hjust=0.5, size=3) +
  geom_rect(data=data.frame(Type="All trials", estimate=0.1, Sex=as.factor("Male"), Outcome="Arousal", Relevance="Relevant"), 
            aes(xmin=0.8, xmax=1.2, ymin=0.5, ymax=0.80), color="#8BC34A", alpha=0) +
  geom_rect(data=data.frame(Type="All trials", estimate=0.1, Sex=as.factor("Female"), Outcome="Arousal", Relevance="Relevant"), 
            aes(xmin=0.8, xmax=1.2, ymin=0.2, ymax=0.5), color="#8BC34A", alpha=0) +
  facet_grid(Outcome~Sex, switch="y") +
  scale_y_continuous(limits=c(0, 1), labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=9, color="black"),
        legend.text = element_text(size = 10),
        legend.position = ) +
  labs(color="Images presented as:",
       tag = "A")
p1
```

>>>>

marginaleffects::avg_slopes(m, variables="Condition", by="Sex", re.form=NA, backend ="emmeans") |> 
  results_table()
```

@@

pred1 <- 
  rbind(
  modelbased::estimate_means(m_arousal, by=c("Sex", "Relevance", "Condition")) |>
  as.data.frame() |> 
  mutate(Outcome="Arousal"),
  modelbased::estimate_means(m_enticement, by=c("Sex", "Relevance", "Condition")) |>
  as.data.frame() |> 
  mutate(Outcome="Enticement"),
  modelbased::estimate_means(m_valence, by=c("Sex", "Relevance", "Condition")) |>
  as.data.frame() |> 
  mutate(Outcome="Valence")
)

@@

p1 <- pred1 |>
  mutate(Sex = fct_relevel(Sex, "Male", "Female")) |> 
  ggplot(aes(x=Relevance, y=estimate)) +
  geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.2) +
  geom_pointrange(aes(ymin = conf.low, ymax=conf.high, color=Condition), position = position_dodge(width=0.2), size=0.2) +
  geom_text(data=stars1, aes(y=y, label=label), hjust=0.5, size=3) +
  geom_rect(data=data.frame(Type="All trials", estimate=0.1, Sex=as.factor("Male"), Outcome="Arousal", Relevance="Relevant"), 
            aes(xmin=0.8, xmax=1.2, ymin=0.5, ymax=0.80), color="#8BC34A", alpha=0) +
  geom_rect(data=data.frame(Type="All trials", estimate=0.1, Sex=as.factor("Female"), Outcome="Arousal", Relevance="Relevant"), 
            aes(xmin=0.8, xmax=1.2, ymin=0.2, ymax=0.5), color="#8BC34A", alpha=0) +
  facet_grid(Outcome~Sex, switch="y") +
  scale_y_continuous(limits=c(0, 1), labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=9, color="black"),
        legend.text = element_text(size = 10),
        legend.position = "bottom") +
  labs(color="Images presented as:",
       tag = "A")
p1
```
